Solar jet observed at the limb in SDO/SST

### 2016-05-24 paper/ms_temp_paper.tex
Add the evolution of shear images

\begin{pycode}[SST_raw]
import numpy as np
from glob import glob
import sunpy.map
import matplotlib.pyplot as plt

im_1 = manager.data_file('core_Ha_dark_165.npy')
im_2 = manager.data_file('core_Ha_dark_170.npy')

afile = np.load(files[])
crop = afile[540:920, 420:610]
val_max = np.max(crop)
plt.imshow(crop, cmap='Greys_r', vmin=0.16*val_max, vmax=val_max, origin='lower', interpolation='none')

@@

>>>>

\begin{pycode}[Bound_SST]
import numpy as np
from glob import glob
import sunpy.map
import matplotlib.pyplot as plt

im_1 = manager.data_file('core_Ha_dark_165.npy')
im_2 = manager.data_file('core_Ha_dark_170.npy')
im_3 = manager.data_file('core_Ha_dark_175.npy')
im_4 = manager.data_file('core_Ha_dark_180.npy')

ims = [im_1, im_2, im_3, im_4]

multi_db = texfigure.MultiFigure(1, 4, reference="demo_bound")
multi_db.caption = "Sequence of images detailing an intermediate phase of the jets evolution. Beggining with a) 07:36:19, b) 07:36:19, c) 07:37:36 and d) 07:38:15"
for i, im in enumerate(ims):
	fig = plt.figure(figsize=texfigure.figsize(pytex, scale=0.25, height_ratio=1.3, figure_width_context='textwidth'))

	afile = np.load(im)
	val_max = np.max(afile)
	plt.imshow(afile, cmap='Greys_r', vmin=0.16*val_max, vmax=val_max, origin='lower', interpolation='none')
	Fig1 = manager.save_figure('demo_bound{}'.format(i+1), fig)
	Fig1.subfig_width = r"0.2\textwidth"
	Fig1.caption = ""
	multi_db.append(Fig1)

@@

\py[Bound_SST]|multi_db|
